Exposing Bugs in JavaScript Engines through Test Transplantation and Differential Testing

### 2020-06-13 paper/paper.tex
pass on technique

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' shows the tests used for
    test transplantation whereas the rectangle under column
    ``no-fail-in-all''---a subset of the ``type-in-all'' tests---shows
    the tests used in cross-engine differential
    testing.}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    %\chakra & \cite{chakra2018repo}\\
    \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    Babel & \cite{babel2020repo} & \babelOriginal{} & \babelPassInPar{} & \babelCompileAll{} & \babelNoFailAll{} \\
    BlogEngine.NET & \cite{babel2020repo} & \blogEngineNetOriginal{} & \blogEngineNetPassInPar{} & \blogEngineNetCompileAll{} & \blogEngineNetNoFailAll{} \\
    \midrule
    %GitHub Projects & - & 494,394 & - & - & - \\
    %\midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

Column ``no-fail-in-all'' shows the tests for which all engines
pass. The set of tests in this column is a subset of the
``type-in-all'' test set. The tests in this set are as fuzzing seeds
in the evaluation of differential testing. The guarantee that they
pass in all engines assures that, if discrepancies occur, they are
related to the changes in the input as opposed to the original cause
of failure. It is worth noting that we also did not include the tests
from \hermes\ in the table because, as the reader shall see in
Table~\ref{tab:test262}, \hermes presents a very low adherence to the
Test262 conformance suite. If we decided to keep \hermes, considering
only the number of passing tests in all engines (the
``no-fail-in-all'' column), it would significantly \Mar{Not sure if I
  understood the conclusion. Do you mean the total amount of test
  (also from other suites)? Why?}reduce our amount of test files.

@@

\lbrack{}Additional cleansing\rbrack{}~We noticed that some of the
tests we found depend on external libraries, which not all selected
engines support. We decided to discard those. For example, many tests
we found were based on Node.js~\cite{node} which\Mar{@Igor, is this
  the reason?  Please, confirm$\rightarrow$}\Igor{yes, it is. Some Node internal features are 
not included in the JS engine, including some keywords (ie. require, module).
In addiction, a project with nodejs require a package.json with a lot of external dependencies.} require libraries to be
installed before running the test and different tests require
different sets of libraries. Also, as already mentioned, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.  Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due.

\lbrack{}Test Harness\rbrack{}~It is also worth mentioning that some
engines uses a custom shell to run tests, including a harness with
specific assertions, \Igor{for example, tests provided by Mozilla contains a lot 
of custom functions (\ie\ assertThrowsInstanceOf, assertEqArray, getPromiseResult).
The shell contains those functions to made the test run correctly.}
\Mar{@Igor, can you name which?}. For that, we
needed to make minor changes in the testing infrastructure to be able
to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable functions, which are only available in
certain engines. Since we had to transplant more than 40k test files,
we tried to mock the minimum amount of code possible to make the test
file work in the other engine.\Mar{This seems a different problem
  (tests without assertions). I did not understand how this is related
  to portability?}\Igor{A test is a simple JS file input.
  Some tests are not well-defined.}  For instance, if a test had a statement such as
\texttt{print(1==1);} we manually refactored that statement to
\texttt{assert(1==1)} which should throw an assertion violation if the condition returns false.
If the change would require more substantial manual work, we opted to discard the test instead. Overall,
we may have manually refactored more than a thousand test files.

@@

Fuzzers are typically categorized in two main groups--those that build
inputs anew (generational) and those that modify existing inputs
(mutational). We used two black-box mutational
fuzzers\Comment{Radamsa~\cite{radamsa} and QuickFuzz~\cite{quickfuzz}}
in this study. In the following, we provide rationale for this
selection.

Generational fuzzers are typically grammar-based. These fuzzers
generate a new file using the grammar of the language whose inputs
should be fuzzed. Intuitively, those fuzzers implement a traversal of
the production rules of the input grammar to create syntax trees,
which are then pretty-printed. Consequently, this approach produces
inputs that are syntactically valid by construction. We analyzed four
grammar-based fuzzers--Grammarinator~\cite{grammarinator},
jsfunfuzz~\cite{jsfunfuzz},
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
were effective out of the box. For example, we produced 100K inputs
with Grammarinator and only few inputs were valid. With Megadeth, we
were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid inputs as it
contains some heuristics to circumvent violations of certain typing
rules.\Comment{ such as \Fix{variable used must be defined?}.}
Nonetheless, running those inputs in our infrastructure we were unable
to find discrepancies. Inspecting those inputs, we realized that they
reflected very simple scenarios. To sum up, a high percentage of inputs
that Grammarinator and Megadeth generated were semantically-invalid
that we needed to discard whereas the valid inputs manifested no
discrepancies. Considering jsfunfuzz~\cite{jsfunfuzz}, we noticed
that, in addition to the issues mentioned above, it produces inputs
that use functions that are only available in the \smonkey{}
engine. We would need either to mock those functions in other engines
or to discard those tests. Considering
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
publicly available. Another fundamental issue associated with
generational fuzzers in our context is that the tests they produce do
not contain assertions; to enable the integration of this kind of
fuzzers in our infrastructure---we would need to look for
discrepancies across compiler error messages as opposed to assertion
violations.  All in all, although grammar-based fuzzers have been
shown effective to find real
bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
fuzzers in this study for the reasons above.

>>>>

\begin{table}[t]
  \small
  \centering
  \caption{\label{tab:test-suites}Number of test files. Dashed
    rectangle under column ``type-in-all'' shows the tests used for
    test transplantation whereas the rectangle under column
    ``no-fail-in-all''---a subset of the ``type-in-all'' tests---shows
    the tests used in cross-engine differential
    testing.}
  \setlength{\tabcolsep}{2pt}
  \begin{tabular}{ccrrrr}
    \toprule
    \multirow{2}{*}{Name}      &  \multirow{2}{*}{Source} &
    \multicolumn{4}{c}{\# JS files} \\
    \cline{3-6}
                               &         & total & pass-in-par. & type-in-all &  no-fail-in-all \\
    \midrule
    Test262 & \cite{ecma262-conformance-suite} & \testOriginal{} & \testPassInPar{} &  \testCompileAll{} & \marktopleft{c2}\testNoFailAll{} \\
    \midrule
    \jsc & \cite{jsc2018repo} & \jscOriginal{} & \jscPassInPar{} &\marktopleft{c1}\jscCompileAll{} & \jscNoFailAll{}\\
    \smonkey\ & \cite{mozilla} & \smOriginal{} & \smPassInPar{} & \smCompileAll{} & \smNoFailAll{}\\
    \veight{} & \cite{v82018repo} & \veightOriginal{} & \veightPassInPar{} & \veightCompileAll{} & \veightNoFailAll{}\\
    %\chakra & \cite{chakra2018repo}\\
    \hermes & \cite{hermes2020repo} & \hermesOriginal{} & \hermesPassInPar{} & \hermesCompileAll{} & \hermesNoFailAll{} \\
    \midrule
    Duktape & \cite{duktape} & \duktapeOriginal{} & \duktapePassInPar{} & \duktapeCompileAll{} & \duktapeNoFailAll{}\\
    \jerry{} & \cite{jerryscript2018repo} & \jerryOriginal{} & \jerryPassInPar{} & \jerryCompileAll{} & \jerryNoFailAll{}\\
    JSI & \cite{jsi} & \jsiOriginal{} & \jsiPassInPar{} & \jsiCompileAll{} & \jsiNoFailAll{}\\
    Tiny-js & \cite{tinyjs} & \tinyOriginal{} & \tinyPassInPar{} & \tinyCompileAll{}\markbottomright{c1} & \tinyNoFailAll{}\markbottomright{c2}\\
    Babel & \cite{babel2020repo} & \babelOriginal{} & \babelPassInPar{} & \babelCompileAll{} & \babelNoFailAll{} \\
    BlogEngine.NET & \cite{blogEngineNet2020repo} & \blogEngineNetOriginal{} & \blogEngineNetPassInPar{} & \blogEngineNetCompileAll{} & \blogEngineNetNoFailAll{} \\
    \midrule
    %GitHub Projects & - & 494,394 & - & - & - \\
    %\midrule
     &  & \totalTestFiles{} & \totalTestFilesPassInPar{} & \totalTestFilesCompileInAll{} & \totalTestFilesPassInAll{}\\
   \bottomrule
  \end{tabular}
\end{table}

@@

Column ``no-fail-in-all'' shows the tests for which all engines
pass. The set of tests in this column is a subset of the
``type-in-all'' test set. The tests in this set are as fuzzing seeds
in the evaluation of differential testing. The guarantee that they
pass in all engines assures that, if discrepancies occur, they are
related to the changes in the input as opposed to the original cause
of failure. 
\Fix{It is worth noting that we also did not include the tests
from \hermes\ in the table because, as the reader shall see in
Table~\ref{tab:test262}, \hermes presents a very low adherence to the
Test262 conformance suite. If we decided to keep \hermes, considering
only the number of passing tests in all engines (the
``no-fail-in-all'' column), it would significantly reduce our amount of test files.}
$\leftarrow$\Breno{Haven't we decided that Hermes should be removed from Table 3? 
If yes, maybe this explanation will only create confusing.}
\Mar{Not sure if I understood the conclusion. Do you mean the total amount of test
  (also from other suites)? Why?}

@@

\lbrack{}Additional cleansing\rbrack{}~We noticed that some of the
tests we found depend on external libraries, which not all selected
engines support. We decided to discard those. For example, many tests
we found were based on Node.js~\cite{node} which
%\Mar{@Igor, is this the reason?  Please, confirm$\rightarrow$}
%\Igor{yes, it is. Some Node internal features are 
%not included in the JS engine, including some keywords (ie. require, module).
%In addiction, a project with nodejs require a package.json with a lot of external dependencies.} 
require libraries to be
installed before running the test and different tests require
different sets of libraries. Also, as already mentioned, we did not
consider tests from the \chakra{} repository because they depend on
non-portable objects.  Finally, note that the number of tests in
\veight\ is low; that happens because \veight{} uses many tests from
Mozilla and \jsc; we discarded those to avoid repetition and to give
credit where it is due.

\lbrack{}Test Harness\rbrack{}~It is also worth mentioning that some
engines uses a custom shell to run tests, including a harness with
specific assertions. For example, tests provided by Mozilla contain a lot 
of custom functions (\eg\ assertThrowsInstanceOf, assertEqArray, getPromiseResult)
and those are included in the shell to make the test run correctly.
For that, we needed to make minor changes in the testing infrastructure to be able
to run the tests uniformly across all engines. More precisely, we
needed to mock non-portable functions, which are only available in
certain engines. Since we had to transplant more than 40k test files,
we tried to mock the minimum amount of code possible to make the test
file work in the other engine.\Mar{This seems a different problem
  (tests without assertions). I did not understand how this is related
  to portability?}\Igor{A test is a simple JS file input.
  Some tests are not well-defined.}  For instance, if a test had a statement such as
\texttt{print(1==1);} we manually refactored that statement to
\texttt{assert(1==1)} which should throw an assertion violation if the condition returns false.
If the change would require more substantial manual work, we opted to discard the test instead. Overall,
we may have manually refactored more than a thousand test files.

@@

%% Fuzzers are typically categorized in two main groups--those that build
%% inputs anew (generational) and those that modify existing inputs
%% (mutational).

Fuzzers are tools for generating inputs for a given input
format~\cite{8863940}. Different fuzzing strategies exist. We analyzed
\emph{generational} and \emph{mutational} fuzzers.

Generational fuzzers create inputs anew, typically following a
language description, typically context-free grammars. Intuitively,
those fuzzers implement a traversal of the production rules of the
grammar to create syntax trees, which are then pretty-printed and used
as a fresh input. Such strategy to create inputs produces inputs that
are syntactically valid by construction. We analyzed four
grammar-based fuzzers--Grammarinator~\cite{grammarinator},
jsfunfuzz~\cite{jsfunfuzz},
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, and
Megadeth~\cite{grieco2016quickfuzz}.  Unfortunately, none of those
were effective out-of-the-box. For example, we produced 100K inputs
with Grammarinator and only few inputs were semantically valid. With
Megadeth, we were able to produce more\Comment{ \Fix{Y, Y$>$Y?}} valid
inputs as it contains some heuristics to circumvent violations of
certain typing rules.\Comment{ such as \Fix{variable used must be
    defined?}.}  Nonetheless, running those inputs in our
infrastructure we were unable to find discrepancies. Inspecting those
inputs, we realized that they reflected very simple scenarios. To sum
up, a high percentage of inputs that Grammarinator and Megadeth
generated were semantically-invalid that we needed to discard whereas
the valid inputs manifested no discrepancies. Considering
jsfunfuzz~\cite{jsfunfuzz}, which has been developed by the Mozilla
team, we noticed that, in addition to the issues mentioned above, it
produces inputs that use functions that are only available in the
\smonkey{} engine. We would need either to mock those functions in
other engines or to discard those tests. Considering
LangFuzz~\cite{Holler:2012:FCF:2362793.2362831}, the tool is not
publicly available. Another fundamental issue associated with
generational fuzzers in our context is that the tests they produce do
not contain assertions; to enable the integration of this kind of
fuzzers in our infrastructure---we would need to look for
discrepancies across compiler error messages as opposed to assertion
violations.  All in all, although grammar-based fuzzers have been
shown effective to find real
bugs~\cite{Holler:2012:FCF:2362793.2362831}, we did not consider those
fuzzers in this study for the reasons above.
